\beginsong{Lady in Black}[by={Uriah Heap}]


\beginverse

\[Em]She came to me one morning, one lonely Sunday morning, Her \[D]long hair flowing in the \[Em]midwinter wind. I know not how she found me for in darkness I was walking and \[D]destruction lay around me from a fight I could not win.

\endverse


\beginchorus

  \[Em]Ah...  ahah.. \[D]ahahah...  \[Em]ahahah, Ah...  ahahah...  \[D]ahahah

\endchorus


\beginverse

\[Em]She asked me name my foe then, I said the need within some men, To \[D]fight and kill their brothers without \[Em]thought of love or God. And I begged her give me horses to trample down my enemies, So \[D]eager was my passion to \[Em]devour this waste of life

\endverse


\beginverse

\[Em]But she would not think of battle that reduces men to animals, So \[D]easy to begin and yet im\[Em]possible to end. For she's the mother of all men who counselled me so wisely then, I \[D]feared to walk alone again and \[Em]asked if she would stay

\endverse


\beginverse

\[Em]Oh, lady lend your hand I cried and let me rest here at your side, "Have \[D]faith and trust in peace", she said and \[Em]filled my heart with life. There is no strength in numbers, have no such misconception, But \[D]when you need me be assured I \[Em]won't be far away

\endverse


\beginverse

\[Em]Thus having spoke she turned away and though I found no words to say, I \[D]stood and watched until I saw her \[Em]black coat disappear. My labour is no easier but now I know I'm not alone, I \[D]find new heart each time I think \[Em]upon that windy day. And if one day she comes to you drink deeply from her words so wise, Take \[D]courage from her as your prize and \[Em]say hello from me.

\endverse

\vfill

\hfill \gtab{Em}{022000} \hfill \gtab{D}{XX0232} \hspace*{\fill}

\endsong

